\documentclass[a4paper,10pt,oneside,openany,final,article]{memoir}
\input{common}
\settocdepth{chapter}
\usepackage{minted}
\usepackage{fontspec}
\setromanfont{Source Serif Pro}
\setsansfont{Source Sans Pro}
\setmonofont{Source Code Pro}

\begin{document}
\title{Update Annex E onto Unicode 15.1}
\author{
  Steve Downey \small<\href{mailto:sdowney@gmail.com}{sdowney@gmail.com}> \\
  \small<\href{mailto:sdowney2@bloomberg.net}{sdowney2@bloomberg.net}> \\
}
\date{} %unused. Type date explicitly below.
\maketitle

\begin{flushright}
  \begin{tabular}{ll}
    Document \#: & D3727R0 \\
    Date: & \today \\
    Project: & Programming Language C++ \\
    Audience: & SG16, CWG
  \end{tabular}
\end{flushright}

\begin{abstract}
  Update the non-normative Annex E to reflect Unicode 15.1 in order to close Core Issue \cite{CWG2843}.
\end{abstract}

\tableofcontents*


\chapter{Introduction}

``Unicode Standard Annex \#31: Unicode Identifiers and Syntax'' for Unicode 15.1 \cite{UAX31-15.1:online} clarifies some of the rules for identifiers and white space syntax.
This paper proposes no normative changes in either area. It simply updates the current Annex E to match the forms used in Unicode Annex 31 as of Unicode 15.1 \cite{unicode_15_1}. See also the differences from Unicode 14 as marked up in \cite{UAX31-15.1-DIFF:online}

\chapter{Proposal}

Strike the reference to R1a Restricted Format Characters. Note that as of Unicode 15.1, \unicode{200d}{zero width joiner} and \unicode{200c}{zero width non-joiner} are part of XID_Continue, and allowed in identifiers.

Replace individual disclaimed conformance points with blanket disclaimer as the conformance list is open ended.

\chapter{Wording}

The proposed changes are relative to \cite{N5008}.

Update Annex E as follows.

\begin{wording}

\include{uax31-new}

\end{wording}

\chapter{Impact on the standard}

No normative change. Modifies non-normative text describing the conformance points with the Unicode Identifier standard.

\chapter*{Document history}

\begin{itemize}
\item \textbf{Initial}
  \begin{itemize}
  \item Rework of P3717R0 on Unicode 15.1
  \end{itemize}
\end{itemize}

\renewcommand{\bibname}{References}
\bibliographystyle{abstract}
\bibliography{wg21,mybiblio}
\end{document}
